---
title: "Project 1:Trends of video game ratings and sales success - Arthur Wu"
output:
  html_document:
    df_print: paged
---

**Loading Packages**

```{r setup}
#load packages
library(tidyverse) # includes ggplot2

## the following two are new.  If you have not yet installed these, comment out the installation lines the first time you run the code.

# install.packages("ggpubr")
library(ggpubr) # containes line/dot plot for visualizing means
#install.packages("descr")
library(descr) ## for "pretty" two-way table CrossTable()

#install.packages("knitr")
library(knitr)
#install.packages("kableExtra")
library("kableExtra")

#install.packages("sjPlot")
library(sjPlot) ## PQ two-way/contingency table
#install.packages("stargazer")
library(stargazer) # PQ numerical summary stats
## installations required to save flextables and ggplot2 objects as imgs
library(webshot)
#install.packages("webshot")
#webshot::install_phantomjs()
```

*loading .csv file*
```{r}
mydata <- read_csv("Video_Games_Sales_as_at_22_Dec_2016.csv")
glimpse(mydata)
```

*cleaning: removing all video games where Year_of_Release < 2001, and converting User_Score to numeric*
```{r}
mydata$Year_of_Release[mydata$Year_of_Release == "1980"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1981"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1982"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1983"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1984"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1985"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1986"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1987"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1988"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1989"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1990"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1991"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1992"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1993"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1994"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1995"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1996"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1997"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1998"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "1999"] <- NA
mydata$Year_of_Release[mydata$Year_of_Release == "2000"] <- NA


vgdata <- mydata %>% drop_na(Year_of_Release, Critic_Score, User_Score)

vgdata$User_Score <- as.numeric(vgdata$User_Score)

saveRDS(vgdata,"P1_data_wu.rds")

glimpse(vgdata)


```




## VARIABLES ##

*Platform Popularity - frequency/percentage table*

```{r, results='asis'}
plat_table <- vgdata  %>% mutate(Platform = fct_infreq(Platform)) %>% ## using fct_infreq to order levels by frequency for the purposes of the chart
              group_by(Platform)  %>% 
              summarize(Frequency = n(),
                        Percentage = n()/dim(vgdata)[1]*100)

plat_table %>% kable(caption = "Table 1: Frequency Distribution of Video Game Platforms") %>% kable_styling(full_width = F)
```

*genre - frequency and percentage table*
```{r}
genre_table <- vgdata  %>% mutate(Genre = fct_infreq(Genre)) %>% ## using fct_infreq to order levels by frequency for the purposes of the chart
              group_by(Genre)  %>% 
              summarize(Frequency = n(),
                        Percentage = n()/dim(vgdata)[1]*100)

genre_table %>% kable(caption = "Table 2: Frequency Distribution of Video Game Genres") %>% kable_styling(full_width = F)


```

*Critic and User scores - summary statistic table stargazer*
```{r}
stargazer(as.data.frame(vgdata), 
          #note you have to specify type html
          type = "html",
          #note that the argument is "out" not "file"
          out = "table3.html",
          title = "Table 3: Summary Statistics of Numerical Variables", # descriptive overall table title
          # relabel variable names to descriptive names
          covariate.labels = c("NA Sales", "EU Sales", "JP Sales", "Other Sales",
                               "Global Sales", "Critic Score", "Critic Count", "User Score", "User Count"),
          digits = 2) # round values to two decimal places

  webshot("table3.html", "table3.png")
```

## Multivariate Analysis ##

*Platform X Critic Score box plot*
```{r}
bold.14.text <- element_text(face = "bold", size = 12) ## define a text style

vgdata %>% 
  mutate(Platform = fct_relevel(Platform, 
            "GBA", "DS", "3DS", "GC", "Wii", "WiiU", 
            "PSP", "PSV", "PS", "PS2", "PS3", "PS4",
            "XB", "X360", "XOne",
            "PC")) %>%
            ggplot(aes(y = Critic_Score, x = Platform, fill = Platform)) + 
                geom_boxplot() +
                theme(legend.position = "none", text = bold.14.text) +
                labs(title = "Figure 1: Distribution of Video Game Critic Score based on Platform",
                    x = "Platform", y = "Critic Score") 

ggsave("fig1_boxplot.jpeg")

```


*Platform X Critic Score group bar graph*
```{r}
mytable <- table(genre = vgdata$Genre, platform = vgdata$Platform)
new_df <- as.data.frame(mytable)

bold.14.text <- element_text(face = "bold", size = 10) ## define a text style

ggplot(new_df, aes(fill=genre, y=Freq, x=platform)) + 
  geom_bar(position="dodge", stat="identity") +

  theme(text = bold.14.text) + ## theme chart with defined text style
  labs(fill="Genre", x = "Platform", y="Frequency", title="Figure 2: Frequency of Video Games per Genre by Platform")

ggsave("fig2_groupbar.jpeg")
```


